---
title: "Lynsey Keator Assignment #7"
output: html_notebook
---

####Question 1
###Create a function that accepts (1) a quantitative response variable, (2) a quantitative explanatory variable, and (3) a number. Suppose we denote the response variable as y, the explanatory variable as x, and the number as p. Your function should model y as a linear function of x and then for each (x,y) pair determine if the residual is one of the p largest in the set of the residuals, with lagest defined in terms of the absolute value (i.e. a residual of -10 is just as large as a residual of 10). The function should return a logical vector indicating TRUE for each pair that has one of the pth largest residuals and FALSE otherwise.

x = explanatory variable
y = response variable
p = a number

```{r}
lm.regressresiduals <-function(x, y, p) {
  regress.model <-lm(y ~ x)
  abs.residuals <- abs(regress.model$residuals)
  sort.residuals <- sort(abs.residuals, decreasing = TRUE)
  cutoff <- sort.residuals[p]
  logical.residuals <- (abs.residuals >= cutoff)
  return(logical.residuals)
}
```

To test the function lm.regressresiduals:

```{r}
x <- c(2, 6, 4, 8, 5, 9, 4)
y <- c(1, 6, 9, 4, 5, 8, 2)

testlm <- lm(x~y)
attributes(testlm)
testlm$residuals
lm.regressresiduals(x, y, 5)

```


####Question 2
###Obtain a real data set with quantitative response and explanatory variables (n>=50). Plot these on a scatterplot with a regression line. Use your function to help you highlight the 10% largest residuals on the scatterplot.

```{r}
library(here)
hsb2 <- read.csv(here("Data", "hsb2.csv"))

#10% of the largest residuals
p <- round(0.1*(nrow(hsb2)))

#Linear Regression Model
model <-lm.regressresiduals(hsb2$read, hsb2$math, 20)

#Correlation
cor <- cor(hsb2$read, hsb2$math)

#Determine which residuals are largest 

residuals <- lm(hsb2$read ~ hsb2$math)
residuals

#Scatterplot with regression line of the linear regression model. Highlighting 10% largest residuals.

plot(hsb2$read, hsb2$math,
     main = "Relationship between Reading and Math Scores",
     xlab = "Reading Score",
     ylab = "Math Score",
     col = ifelse(model == TRUE, "blue", "black"),
     pch = ifelse(model == TRUE, 15, 0))

abline(residuals)
```

